\documentclass[a4paper]{arthur-letter}
\title{I think I'm being unjustly smeared by Dianna Cowern, AKA Physics Girl}
\author{Matthew Woods, FKA Burns}

\usepackage[english]{babel}
\usepackage{fontspec}
\usepackage{luatexbase}
\usepackage{microtype}

% only needed for the example
\usepackage{lipsum}

%%=================%%
%%  Custom colors  %%
%%=================%%

% \definecolor{boxcolor}{HTML}{0E5484}
% \definecolor{maincolor}{HTML}{1a4c70}
% \definecolor{secondcolor}{HTML}{4d4d4d}

%%==========%%
%%  Header  %%
%%==========%%

% Set profile info [Following information are optional]
\letname{Matthew Woods}            % Your full name
\linkedin{matthew-woods-75bb721a5}       % Your linkedin
\mail{mattwoods243@gmail.com}       % Your email
\numberphone{408-613-3406}                % Your phone number
\lettitle{Alphabet Inc Lies, Blacklists and Conspiracy} % Title of your letter
\site{xignalx.com}                       % Your site
\github{}
\profilepic{}

\begin{document}
    \makeprofile % Set header
    
    % English commands (address and location at right and recipient at left)
    \address{Matthew Woods,\\PO Box 376\\Mountain View, CA}

    \begin{letter}

            \subject{I'm a former Navy SEAL, smeared by Dianna Cowern (AKA Physics Girl) via Alphabet Inc while working as a Google employee.}

            \opening{Dear New York Times,}

            For this story to make sense, I have to go back to the year 2013, when Dianna Cowern emailed me in response to a Craigslist ad that I placed for a male roommate. She replied, "What if it's a really cool girl?". I let her come see the house and she seemed fine, so I let her move in. We lived under the same roof for over two years, save a six month period where I provided anti-piracy contracting services to Maersk via The Trident Group as an APASS operator. When I met her the first time, she casually mentioned that she was from Kauai, where I already had a future flight booked for vacation with my then girlfriend. She also mentioned that she had been living with a group of SEALs prior to then... lot of coincidences. It is my belief that she was working with them and others (my family, the VA and other SEALs that I know) to defraud me and smear my name. I don't have a clear motive, probably money. She mentioned once that she "thought about joining the CIA", which makes me suspicious of the CIA as well. I applied to the CIA in 2007 as a SEAL and never heard anything. I was granted TS/SCI in 2008 in order to attend some SEAL schools, but was never read in on any programs. I never made contact with a CIA person, until Google in 2019. I did however try to apply as a GRS operator (SOC USA), only to find that they only accept operators who have an active clearance. Mine had expired, having been in school the previous four years. \\ 
            
            Inviting her in was a huge mistake. At this point (2013), I was separated from the Navy for four years, during which I earned my BS in Electrical Engineering and began applying to graduate school for the same. During my service as a SEAL, I saw combat in Iraq and the Philippines. Being a mediocre SEAL, I decided to leave and try something more in line with my then perceived strengths: math and scientific computing. I was living with friends at the time in a four bedroom house in Pacific Beach, CA (5328 Westknoll Dr). My "good friend" Garett McDermid offered me the room since he was moving for some reason. I think he was part of some setup, working with my then family, which I will get to later. I no longer associate with those people (Burns), opting to change my name to Woods in honor of Ty Woods in 2019. There are many characters in this story, but I will keep the focus on Dianna for the time being. After a month of living there, she introduced me to her SEAL buddies that she was supposedly living with before. They were new guys, just back from first deployment. They informed me that they nicknamed her "Dirty", the nickname of a famous SEAL that I was friends with at the time. I asked them, and they confirmed that they knew him. What is strange is that the original Dirty is quite evil and I never trust him. He is a war hero, though, in my eyes. He's most likely a psychopath. I think that was my first clue that something was off with this girl. If she is what I think she is, psychopath is a workable label. She may be a Nazi. My parents, on the other hand, are almost certainly Nazis, although I have not caught them doing anything illegal yet. I know this because they are my parents and have said many things over the years (e.g. Donald Burns: "I wonder if they will ever make a movie about WWII that is from the German side"). Dianna, I suspect by association, she never did anything to me overtly. Her parents may have been in contact with my parents and convinced her to do something. \\
            
            The main event with Dianna comes in 2015. Something bad happened to me that year, probably some kind of Nazi attack. I became mentally unwell, fell in love with her and proposed all within a short period of time. I had no idea what she was... I thought friend and roommate of several years. I could not have been more wrong. She enacted a restraining order, which you can research with this link: \url{http://courtindex.sdcourt.ca.gov/CISPublic/casedetail?casenum=DV041758&casesite=SD&applcode=D}. I can read it today and laugh, but it bothered me for years that I couldn't explain what happened. Long story short, the contents of the restraining order contain factual information about what happened. It was put together by the physics students we were living with, including Dianna. It is extremely misleading. During that time, someone was anonymously calling the police on me almost every day in my home for "Wellness checks." I was being put in handcuffs a lot, but they never had any reason to arrest me. My Nazi roommates begged me to go to the VA for observation, since I was not behaving how they wanted me to behave. That is when I met Dr. Lehman of the VA La Jolla and a woman who never showed her face again (older, glasses, purple coat). Upon entry, she made care to say, "We don't ask about war crimes." It never sat right with me that she said that. "WTF is that supposed to mean?". Based purely on the testimony of these kids, the VA assigned me a diagnosis of Bipolar II, which I believe is false. I have struggled with depression for years, but that episode, at 32 years old, was the direct result of some kind of assault on me in plain view of the public. They are trying to create a narrative that I am mentally unwell in general, which is false. It is my goal to sue the VA and have everything they have written wiped from the electronic record. I went to the FBI in 2015 complaining of Nazis in the VA. They ignored me. \\
            
            
            

            \closing{Yours sincerly,} % To adapt following recipient

            \signing{Matthew Woods (FKA Burns)}

    \end{letter}

\end{document}